Research Experience

### 2010-02-17 doc/thesis/thesis.tex
changed default output for calc_parammap. Eval now uses spacing/orientation.

\begin{document}

>>>>

\begin{document}
\section*{Introduction}
Nuclear Magnetic Resonance Imaging is a powerful tool in the analysis
of both brain struction as well as activity. In particular Functional
MRI gives very high spatial resolution at the cost of rather limited
temporal resolution. Whereas other methods
of analyzing neural signals can be invasive or ill-posed, 
FMRI is relatively easy, and its analysis straight forward. Because of
these benefits, FMRI has great potential for studying human cognition.
Unfortunately, in order to achieve the speeds necessary to catch the
Blood Oxygen Level Dependent (BOLD) signal, very little time can
be spent allowing NMR spin to settle out, nor can much time be spent
gathering a large region in K-Space. Because of these restrictions,
FMRI is plagued with unidentified noise (cite) and offers a temporal
resolution on the order of seconds rather than milliseconds.

Traditional methods of analyzing FMRI images are ad-hoc and in many
ways arbitrary. Data is often thrown out due to a lack of activation (cite),
and there is no standard method of removing the low frequency drift
present in all such images. Often times "activations" are looked at
individually by taking the percent difference between the "activated"
signal and the signal just before a stimulus was applied. Another popular
method is a direct highpass filter, but this can attenuate actual
signal, and introduce high frequency artifacts (cite).

The traditional method of analyzing FMRI data is to use the average
over multiple runs,
